---
title:           2018-HIM3HIB / HIM5IHB Stats and grades
author:          Dennis Wollersheim 
date:            16.06.2018
linkcolor:       cyan
citecolor:       grey
output:
  pdf_document:
    highlight:   zenburn
  word_document:
    reference_docx: /code/R/knitr-styles/word_reference_style_landscape.docx
    fig_width: 10
    fig_height: 6.5
---


```{r init_data, results='hide', message=FALSE, warning=FALSE, echo=FALSE, comment=NA }

source('lib/functions.R')
opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE, comment=NA) 
marks_root = '2018-HIM3HIB'
private=FALSE
pdf=FALSE
weeks_semester_start = 30

data = get_data( marks_root )
log = data[['log']]
class_name = data[['class_name']]
marks = data[['marks']]

```

# Marks for the class `r  class_name`
For the period : `r log %>% summarise( min(time), max(time)) `
---
`r if (!private) '## Overall LMS participation by student'`


```{r introduction }

if (private)  {
  # overall
  log %>%
    group_by( semester_week ) %>%
    count( user_full_name, component ) %>%
    ggplot( aes( semester_week, n, fill=component)) +
    geom_col() +
    facet_wrap( ~user_full_name, ncol=3) 

}
```

## Summary LMS participation by student
---


```{r Summary_by_student_last_digit }

log %>%
  group_by( semester_week ) %>%
  count( user_full_name, student_id_final_digit ) %>%
  ggplot( aes( semester_week, n)) +
  geom_line( aes( group = user_full_name, color=student_id_final_digit)) +
  ggtitle( "Number of LMS visits per week by student, identified by student id last number")

log %>%
  mutate( semester_week = as.factor(semester_week) ) %>%
  group_by( semester_week ) %>%
  count( subject_code, user_full_name, student_id_final_digit ) %>%
  group_by( semester_week, subject_code ) %>%
  mutate(outlier = ifelse(is_outlier(n), student_id_final_digit, as.character(NA))) %>%
  #filter( !is.na(outlier)) %>%
  ggplot( aes( semester_week, n, fill=subject_code)) +
  geom_boxplot( ) +
  ggtitle( "Number of LMS visits per week for whole class")


if (pdf) {
  # overall
  log %>%
    group_by( semester_week ) %>%
    count( user_full_name, component ) %>%
    ggplot( aes( semester_week, n, fill=component)) +
    geom_col() +
    facet_wrap_paginate( ~user_full_name, ncol=3, nrow=3) %>% 
    { . } ->  p
    class(p) <- c('gg_multiple', class(p))
    print(p)
}
```

# access to each component over the semester

```{r}

log %>% 
  count( component ) %>%
  top_n( 5)  -> top5_component
#
log %>%
  filter( component %in% top5_component$component ) %>%
  group_by( semester_week ) %>%
  count( user_full_name, component ) %>%
  ggplot( aes( semester_week, n, fill=component)) +
  geom_col() +
  facet_wrap( ~component, ncol=2) +
  ggtitle ("what portion of LMS do people access")

```


LMS accesses in Victoria, off campus

```{r }

area <- read_shape("~/mydoc/research/mofi/shapefiles/LGA11aAust.shp") 
area %>% 
  subset( STATE_CODE==2 )  %>% 
  {.} -> vic_area
#
vic_area %>% simplify_shape(0.1) %>%
  {.} -> vic_simp
#

reorder_size <- function(x) {
  factor(x, levels = names(sort(table(x))))
}

log %>%
  filter( isp != 'Latrobe University' &
         city_name != 'Melbourne'  &
         city_name != 'Bundoora' ) %>% 
inner_join( count( ., city_name ) %>% top_n( 20) ) %>%
mutate( city_name = reorder_size( city_name )) %>%
count(city_name, subject_code  ) %>%
ggplot(aes(city_name, y=nn, fill=subject_code)) +
geom_col() + 
xlab('City Name') +
ylab('Number of accesses') +
rotate() +
ggtitle( 'Top 20 localities for access LMS from off campus')



log %>%
  filter( isp != 'Latrobe University' &
         city_name != 'Melbourne'  &
         city_name != 'Bundoora' ) %>% 
inner_join( count( ., city_name ) %>% top_n( 20) ) %>%
mutate( city_name = reorder_size( city_name )) %>%
count(city_name, semester_week  ) %>%
ggplot(aes(city_name, y=nn, fill=semester_week)) +
geom_col() + 
xlab('City Name') +
ylab('Number of accesses') +
rotate() +
ggtitle( 'Top 20 localities for access LMS from off campus')



```

`r if (!private) '# non bundoora / melbourne / latrobe cities'`

```{r }

if (private) {
  log %>%
    filter( isp != 'Latrobe University' &
           city_name != 'Melbourne'  &
           city_name != 'Bundoora' ) %>% 
  ggplot(aes(reorder_size( city_name), fill=user_full_name)) +
  geom_bar() + 
  rotate()
}
```

# which ISP's 

```{r }

log %>%
  ggplot(aes(reorder_size( isp), fill=country_code)) +
  geom_bar() + 
  rotate() + 
  ggtitle( 'ISPs accessing LMS') +
  xlab( 'ISP') + ylab( 'Number of accesses')


```

#LMS accesses from inside Victoria

```{r }

log %>% 
  filter( as.character( zip_code ) %>% startsWith('3') ) %>%
  filter( country_code=='AU' & isp != 'Latrobe University' ) %>% 
  count(  longitude, latitude, semester_week ) %>% 
  mutate( logn=log10( n ) ) %>%
  SpatialPointsDataFrame(coords = .[,1:2], data=., proj4string=CRS("+proj=longlat +datum=WGS84")) %>% 
  { . } -> pts

tm_shape(vic_simp) +
  tm_borders() + 
  tm_shape( pts ) +
  tm_bubbles( size='logn', col='semester_week'  ) +
  tm_style_gray() + 
  tm_format_World() +
  tm_layout("LMS accesses inside victoria")

```

#LMS accesses from outside the Australia

```{r }
data(World)

log %>% 
  filter( country_code != 'AU'  ) %>%
  count(longitude, latitude, user_full_name, semester_week ) %>% 
  mutate( logn=log10( n ) ) %>%
  SpatialPointsDataFrame(coords = .[,1:2], data=., proj4string=CRS("+proj=longlat +datum=WGS84")) %>% 
  { . } -> users

#
tm_shape(World) +
  tm_borders() + 
  tm_shape( users ) +
  tm_bubbles( size='logn', col='semester_week') +
  tm_style("gray") + 
  tm_format("World") +
  tm_layout("LMS accesses outside Australia")

#tmap_mode("plot")

eval_cell=TRUE
if (!(sum(marks$subject_total_real, na.rm=TRUE) > 0 )) {
  eval_cell = FALSE
}

```


`r if (eval_cell) '# total access vs marks for 5 most accessed components'`

```{r   eval=eval_cell  }
# access vs marks

log %>%
  filter( component %in% top5_component$component ) %>%
  count( user_full_name, component )  %>%
  inner_join( marks ) %>%
  ggplot( aes(subject_total_real, n)) +
  xlab( "Total Subject Mark") +
  ylab( "Number of LMS Accesses ") + 
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap( ~component, scales='free_y', ncol=2 )

```

`r if (eval_cell) '# access vs marks overall by person'`

```{r  eval=eval_cell }


log %>%
  count( user_full_name)  %>%
  inner_join( marks ) %>%
  ggplot( aes(subject_total_real, n)) +
  xlab( "Total Subject Mark") +
  ylab( "Number of LMS Accesses ") + 
  geom_smooth() +
  geom_text(aes(label=user_full_name)) +
  geom_point()



```

`r if (eval_cell) '# access vs marks overall by person and week'`


```{r  eval=eval_cell }

log %>%
  count( user_full_name, semester_week)  %>%
  inner_join( marks ) %>%
  ggplot( aes(subject_total_real, n)) +
  xlab( "Total Subject Mark") +
  ylab( "Number of LMS Accesses ") + 
  geom_smooth() +
  geom_text(aes(label=substr(user_full_name,1,5))) +
  geom_point() +
  facet_wrap( ~semester_week, scales='free_y', ncol=3 )



log %>%
  count( user_full_name, component)  %>%
  inner_join( marks ) %>%
  ggplot( aes(subject_total_real, n)) +
  xlab( "Total Subject Mark") +
  ylab( "Number of LMS Accesses ") + 
  geom_smooth() +
  geom_text(aes(label=substr(user_full_name,1,5))) +
  geom_point() +
  facet_wrap( ~component, scales='free_y', ncol=3 )


log %>%
  count( user_full_name, component)  %>%
  inner_join( marks ) %>%
  ggscatter( x='subject_total_real',y= 'n',
            add = "reg.line", conf.int = TRUE, 
            cor.coef = TRUE, cor.method = "pearson",
            ) +
xlab( "Total Subject Mark") +
ylab( "Number of LMS Accesses ") + 
facet_wrap( ~component, scales='free_y', ncol=3 )




log %>%
  count( user_full_name, semester_week)  %>%
  inner_join( marks ) %>%
  ggscatter( x='subject_total_real',y= 'n',
            add = "reg.line", conf.int = TRUE, 
            cor.coef = TRUE, cor.method = "pearson",
            ) +
  xlab( "Total Subject Mark") +
  ylab( "Number of LMS Accesses ") + 
  facet_wrap( ~semester_week, scales='free_y', ncol=3 )

}

